\section{Introduction}

Palmprint recognition is commonly evaluated as an identification and verification problem. Early online palmprint systems established the feasibility of palmprint-based personal identification \cite{zhang2003online}, while later surveys organized the field around acquisition devices, preprocessing, feature extraction, matching, fusion, and privacy/security issues \cite{kong2009survey,fei2019feature}. Recent deep-learning surveys describe a broad shift from handcrafted texture descriptors toward learned feature representations for ROI processing, feature extraction, matching, and robustness analysis \cite{gao2025deeplearning}. Contactless and cross-session recognition remain difficult because acquisition changes can alter illumination, pose, deformation, ROI quality, and sensor conditions between recording sessions. Existing palmprint work increasingly adopts deep representation learning and components inspired by face recognition or person re-identification. However, a component that improves a seen-identity diagnostic split may not preserve its ranking under held-out-palm, cross-session evaluation, particularly when deployment-relevant low-FAR behavior is measured. This paper therefore asks whether conclusions about BNNeck and ArcFace remain stable when the protocol is made palm-class-disjoint and bidirectional across Tongji sessions.

This paper studies a narrow but important protocol question: whether improvements observed for standard deep embedding components under a seen-identity diagnostic setting persist when the development and test palm classes are separated. The distinction matters for biometric evaluation. If development and test identities overlap, a model can appear stronger than it is under a held-out-identity or held-out-palm deployment setting. The Tongji dataset supports an explicit cross-session analysis because the repository protocol separates S1$\rightarrow$S2 and S2$\rightarrow$S1 directions, enabling evaluation under acquisition shift.

The starting hypothesis was that BNNeck \cite{luo2019strong} and ArcFace \cite{deng2019arcface}, two components that are effective in person re-identification and face recognition, may improve ResNet18 palmprint embeddings over a cross-entropy plus supervised-contrastive baseline \cite{khosla2020supervised}. The strict results do not support that hypothesis as a general improvement claim. BNNeck + ArcFace appears favorable in the original seen-identity Tongji diagnostic setting, but under the stricter development/test palm-class-disjoint Tongji protocol it trails CE + SupCon by 1.18 percentage points in bidirectional three-seed Rank-1 and has an EER that is 1.01 percentage points worse.

The stronger component-level observation is more specific: BNNeck with standard cross-entropy supervision has the highest observed mean among the tested variants on the main strict Tongji Rank-1 and TAR@FAR=$10^{-3}$ metrics, whereas ArcFace-based variants are not consistently beneficial. The corrected IITD palm-class-disjoint within-session rerun provides secondary validation and shows a near-tie between CE + SupCon and BNNeck + ArcFace rather than a clear BNNeck + ArcFace advantage. The resulting contribution is therefore not a new architecture and not a claim of state-of-the-art performance. It is a controlled, protocol-sensitive evaluation showing that a favorable seen-identity conclusion for BNNeck + ArcFace does not transfer cleanly to palm-class-disjoint cross-session evaluation.

The contributions of this paper are:
\begin{itemize}
    \item A strict palm-class-disjoint cross-session evaluation of ResNet18 palmprint embeddings on Tongji across S1$\rightarrow$S2 and S2$\rightarrow$S1 directions and three random seeds.
    \item A protocol-sensitivity analysis showing that BNNeck + ArcFace appears favorable in the original seen-identity diagnostic setting but does not consistently improve under held-out palm-class evaluation.
    \item A component ablation over CE, SupCon, BNNeck, ArcFace, and light SupCon variants, showing that BNNeck + CE has the highest observed mean on the selected strict-protocol metrics while ArcFace-based variants are unstable or weaker.
    \item A corrected IITD palm-class-disjoint within-session secondary validation showing a near-tie between CE + SupCon and BNNeck + ArcFace rather than a clear BNNeck + ArcFace improvement.
\item A palmprint-specific fixed-Gabor texture reference baseline evaluated under the same strict Tongji gallery/probe splits, showing that classical texture features remain competitive for Rank-1 but are much weaker for low-FAR verification.
    \item Reproducible split hashes, protocol-audit summaries, checkpoint-selection evidence, metric-threshold evidence, configs, and result summaries for the scoped evaluation.
\end{itemize}
