\section{Related Work}

\subsection{Palmprint Recognition}

Palmprint recognition has a long history as a biometric identification and verification modality. Zhang et al. introduced an online palmprint identification system that combined a dedicated acquisition device with an efficient recognition algorithm \cite{zhang2003online}. Subsequent surveys summarized the broader palmprint pipeline, including capture devices, preprocessing, verification algorithms, fusion, large-database identification, and privacy/security issues \cite{kong2009survey}. More recent survey work evaluates feature-extraction methods across contact-based, contactless, high-resolution, and 3D palmprint scenarios \cite{fei2019feature}, while a deep-learning-focused survey describes the transition from handcrafted descriptors toward learned ROI, representation, matching, and security/privacy components \cite{gao2025deeplearning}.

Classical palmprint methods often exploit local line and orientation structure. Competitive Code is a representative direction-coding method that encodes dominant local orientations using a bank of Gabor filters and angular matching \cite{kong2004competitive}. This orientation-coding lineage is relevant because palmprint texture is dominated by principal lines, wrinkles, creases, and ridge-like structures. Modern deep palmprint methods have also reused this bias: PalmNet tunes palmprint-specific filters through Gabor-PCA convolutional filters \cite{genovese2019palmnet}, and CompNet introduces learnable Gabor kernels in a competitive neural-network formulation \cite{liang2021compnet}. These works motivate reporting Gabor-related baselines, but they do not justify treating fixed Gabor filtering as the primary contribution of the present paper.

Contactless palmprint recognition is more difficult than contact-based recognition because pose, scale, rotation, illumination, background, and session conditions are less controlled. Tongji was introduced as a contactless palmprint benchmark together with a contactless acquisition device and a collaborative-representation-based identification approach \cite{zhang2017tongji}. Wider reviews of unconstrained and consumer-device palmprint recognition emphasize that ROI extraction, feature learning, matching, and dataset protocol design remain central sources of variation \cite{ungureanu2020toward}. The present paper therefore focuses on a narrower but directly testable question: whether conclusions about BNNeck and ArcFace remain stable when moving from a seen-identity diagnostic setting to a palm-class-disjoint Tongji cross-session protocol.

\subsection{Metric Learning for Biometric Embeddings}

Biometric recognition systems depend on embedding geometry: genuine pairs should remain close while impostor pairs should be separated, especially at strict false-acceptance operating points. Supervised contrastive learning explicitly pulls same-class examples together and pushes different-class examples apart \cite{khosla2020supervised}. The B1 baseline in this project uses this idea together with cross entropy, forming a strong baseline for the Tongji cross-session protocol.

Margin-based normalized classifiers provide another route to discriminative embeddings. ArcFace adds an angular margin to normalized features and class weights, encouraging separation in angular space \cite{deng2019arcface}. BNNeck was introduced in person re-identification as a normalization neck that separates feature spaces used for metric comparison and classification supervision \cite{luo2019strong}. B6 adapts these two ideas to the palmprint setting: ArcFace shapes the angular classifier geometry, while BNNeck provides the post-BN embedding used for cosine verification.

\subsection{Cross-Session and Protocol-Sensitive Evaluation}

Cross-session and cross-domain robustness are central issues for deployable biometric systems. Contactless and unconstrained palmprint studies show that performance can depend strongly on acquisition condition, ROI quality, and evaluation design \cite{ungureanu2020toward,matkowski2020uncontrolled}. Broader palmprint robustness research includes domain adaptation, style-transfer, synthetic-data, mobile-device acquisition, and cross-dataset evaluation directions \cite{zhang2020smartphone,shao2020efficient}. This paper does not attempt to benchmark all of those settings. Instead, it focuses on Tongji cross-session recognition with S1$\rightarrow$S2 and S2$\rightarrow$S1 protocols. The results should therefore be read as evidence for the scoped Tongji cross-session evaluation, not as a broad cross-domain benchmark claim. External datasets and verified cross-domain comparisons remain future work.

\subsection{Protocol Positioning Relative to Palmprint Literature}

Representative palmprint studies differ substantially in acquisition setup, ROI construction, gallery/probe definition, session use, and reported operating points. Table~\ref{tab:literature_protocol_positioning} therefore positions this work relative to prior palmprint literature by protocol properties rather than by direct numerical ranking.

\begin{table*}[t]
\centering
\caption{Protocol positioning relative to representative palmprint recognition studies. The table contextualizes protocols rather than claiming direct numerical comparability.}
\label{tab:literature_protocol_positioning}
\small
\setlength{\tabcolsep}{3pt}
\begin{tabular}{p{0.15\textwidth}p{0.18\textwidth}p{0.19\textwidth}p{0.10\textwidth}p{0.13\textwidth}p{0.17\textwidth}}
\toprule
Study & Representation & Dataset(s) & Contactless & Cross-session & Directly comparable? \\
\midrule
Zhang et al.~\cite{zhang2017tongji} & CR CompCode & Tongji & Yes & Yes & Partially; protocol differs \\
PalmNet~\cite{genovese2019palmnet} & Gabor-PCA CNN & Multiple touchless sets & Yes & Not normalized here & No \\
CompNet~\cite{liang2021compnet} & Learnable Gabor CNN & Multiple palmprint sets & Yes & Not normalized here & No \\
Matkowski et al.~\cite{matkowski2020uncontrolled} & Alignment + feature network & IITD/CASIA/PolyU/NTU & Yes & Mixed & No \\
Smartphone verification~\cite{zhang2020smartphone} & DCNN verification pipeline & Smartphone palmprint data & Yes & Yes & No \\
Ours & BNNeck/ArcFace matrix + Gabor ref. & Tongji + IITD & Yes & Tongji yes & Current protocol \\
\bottomrule
\end{tabular}
\end{table*}

Because prior studies differ in ROI pipelines, train/test identity assumptions, gallery construction, session use, and reported metrics, this table is not used as a leaderboard. It motivates why the present work focuses on a controlled within-paper component matrix under one audited protocol.
