\section{Audited Protocol and Component Matrix}

We do not introduce a new architecture. Instead, we define a controlled component matrix that probes selected effects and interactions of cross-entropy, supervised contrastive learning (SupCon), BNNeck, and angular-margin heads (ArcFace, CosFace) under identical backbone, optimizer, embedding dimensionality, checkpoint-selection, and evaluation protocols.

\subsection{Component Matrix and Evaluation Scope}

This work evaluates a controlled family of ResNet18 embedding models rather than proposing a new palmprint architecture. All tested learned variants use the same backbone family and a 256-D embedding size; they differ only in their recognition heads, neck layers, and loss terms. The main configurations evaluated are:
\begin{itemize}
    \item \textbf{M0}: ResNet18 + Cross-Entropy (CE);
    \item \textbf{M1}: ResNet18 + CE + Supervised Contrastive Learning (SupCon);
    \item \textbf{M2}: ResNet18 + ArcFace;
    \item \textbf{M3}: ResNet18 + CosFace;
    \item \textbf{M4}: ResNet18 + BNNeck + CE;
    \item \textbf{M6}: ResNet18 + BNNeck + ArcFace;
    \item \textbf{M7}: ResNet18 + BNNeck + ArcFace + light SupCon.
\end{itemize}
Here, M1 is the standard CE + SupCon baseline. M6 is the initially hypothesized BNNeck + ArcFace configuration because it appeared highly favorable in the seen-identity diagnostic setting. M4 is included to probe selected effects and interactions of BNNeck without ArcFace, while M3 incorporates CosFace to evaluate alternative angular-margin formulations. The strict Tongji component matrix is used to distinguish the original M6 hypothesis from the broader component behavior observed under palm-class-disjoint evaluation.

\subsection{BNNeck Embedding}

BNNeck was proposed as a normalization neck for separating the feature space used for metric comparison from the feature space optimized by classification supervision \cite{luo2019strong}. Let $h_i$ denote the output feature of the ResNet18 backbone for sample $i$. A linear projection maps this feature to a 256-D vector:
\begin{equation}
    z_i = W_e h_i + b_e.
\end{equation}
BNNeck applies batch normalization to this projected vector:
\begin{equation}
    \tilde{z}_i = \mathrm{BN}(z_i).
\end{equation}
For BNNeck variants, the evaluation embedding is the post-BN representation:
\begin{equation}
    f_i = \frac{\tilde{z}_i}{\lVert \tilde{z}_i \rVert_2}.
\end{equation}
For non-BNNeck variants, the corresponding 256-D embedding is L2-normalized before matching. Gallery and probe embeddings are compared with cosine similarity.

\subsection{Angular-Margin Supervision}

ArcFace uses normalized features and normalized class weights to impose an additive angular margin \cite{deng2019arcface}. Let $W_j$ be the normalized classifier weight for class $j$, and let $\theta_j$ be the angle between the normalized embedding $f_i$ and $W_j$. For the ground-truth class $y_i$, ArcFace adds an angular margin $m$ and scales logits by $s$:
\begin{equation}
    \ell_i =
    -\log
    \frac{
        \exp \left(s \cos(\theta_{y_i} + m)\right)
    }{
        \exp \left(s \cos(\theta_{y_i} + m)\right)
        + \sum_{j \ne y_i} \exp \left(s \cos(\theta_j)\right)
    }.
\end{equation}
In the current M6 configuration, $s=30.0$ and $m=0.5$. CosFace (M3) similarly imposes an additive cosine margin:
\begin{equation}
    \ell_i =
    -\log
    \frac{
        \exp \left(s (\cos\theta_{y_i} - m)\right)
    }{
        \exp \left(s (\cos\theta_{y_i} - m)\right)
        + \sum_{j \ne y_i} \exp \left(s \cos\theta_j\right)
    }.
\end{equation}
with $s=30.0$ and $m=0.35$. The experiments test whether these training geometries actually improve held-out palm-class verification and identification metrics under cross-session acquisition shifts.
