\section{Experimental Setup}

\subsection{Datasets and Protocols}

The primary evaluation uses the segmented Tongji palmprint dataset \cite{zhang2017tongji}. The repository manifest contains 12,000 Tongji images from 600 palms/classes, with 6,000 images in session 1 and 6,000 images in session 2. The recorded image size is $128 \times 128$. We evaluate two cross-session directions:
\begin{itemize}
    \item S1$\rightarrow$S2: training, validation, and gallery data from session 1; probe data from session 2.
    \item S2$\rightarrow$S1: training, validation, and gallery data from session 2; probe data from session 1.
\end{itemize}
The main reported Tongji numbers are bidirectional averages over S1$\rightarrow$S2 and S2$\rightarrow$S1 with seeds 42, 2026, and 2705.

The IITD palm-class-disjoint within-session protocol is used as secondary validation. The repository manifest contains 2,601 IITD images from 460 palms/classes \cite{iitd_touchless_palmprint}, with all samples recorded as session 1 and image size $150 \times 150$. Splits are constructed over seeds 42, 2026, and 2705. Because IITD is single-session in the current manifest, it is interpreted as within-session palm-class-disjoint validation rather than cross-session evidence.

\begin{table}[t]
\centering
\scriptsize
\setlength{\tabcolsep}{4pt}
\caption{Dataset split sizes and classes/subjects partitioning used by the experiments. For IITD, split sizes vary slightly across seeds; values for Seed 42 are reported.}
\label{tab:split_sizes}
\begin{tabular}{lrrrrcc}
\hline
Protocol & Train (Images) & Val (Images) & Gallery (Images) & Probe (Images) & Dev Classes & Test Classes \\
\hline
Tongji S1$\rightarrow$S2 (Disjoint) & 3,840 & 960 & 1,200 & 1,200 & 480 & 120 \\
Tongji S2$\rightarrow$S1 (Disjoint) & 3,840 & 960 & 1,200 & 1,200 & 480 & 120 \\
IITD within (Disjoint) & 1,670 & 417 & 238 & 276 & 368 & 92 \\
\hline
\end{tabular}
\end{table}

\input{../docs/audits/rankb_protocol_audit_table.tex}

Palm-class and subject-ID fields are parsed from the repository manifest before split construction. The identity/parser audit documents the manifest fields used for \texttt{path}, \texttt{session}, \texttt{hand}, \texttt{subject\_id}, \texttt{palm\_id}, \texttt{class\_id}, and \texttt{sample\_id}. For each seed, it verifies zero image-level, palm-class, palm-ID, and subject-ID overlap between development and held-out test partitions. Because the repository does not provide an independently verified person-level identifier beyond the manifest fields, the final claim remains conservatively scoped as palm-class-disjoint rather than person-disjoint.

A gallery/probe construction audit further verifies the held-out evaluation partitions. For Tongji, S1$\rightarrow$S2 uses session 1 as gallery and session 2 as probe, while S2$\rightarrow$S1 reverses this direction. For the corrected IITD within-session split, every held-out palm class appears in both gallery and probe with zero image overlap. IITD therefore remains secondary within-session validation rather than cross-session evidence.


\subsection{Compared Methods}

The main strict-protocol comparison focuses on the pre-specified B1/B6 pair because B1 is the current CE + SupCon baseline and B6 is the BNNeck + ArcFace variant evaluated as the principal method hypothesis. Section~\ref{sec:ablation} additionally reports a complete strict Tongji component ablation over B0, B1, B4, B5, B6, and B7 across both session directions and three seeds. Fixed-Gabor variants are discussed as related baselines but are outside the current strict-protocol component-ablation matrix.

\subsection{Training Recipe}

The common training recipe used by the final compared Tongji runs is:
\begin{itemize}
    \item epochs: 60;
    \item learning rate: $1 \times 10^{-4}$;
    \item weight decay: $1 \times 10^{-4}$;
    \item embedding dimension: 256;
    \item automatic mixed precision: enabled;
    \item gradient accumulation steps: 4;
    \item identity sampler: 8 identities and 2 instances per identity, with fallback identities set to 4;
    \item data loader workers: 0;
    \item Tongji seeds: 42, 2026, 2705.
\end{itemize}

B0 uses ResNet18 with cross entropy only. B1 adds supervised contrastive learning with $\lambda_{\mathrm{supcon}}=0.10$ and temperature 0.07. B4 uses ResNet18 with ArcFace supervision. B5 uses ResNet18 + BNNeck with cross entropy only. B6 uses ResNet18 + BNNeck + ArcFace, with ArcFace scale $s=30.0$, margin $m=0.5$, $\lambda_{\mathrm{supcon}}=0.0$, and temperature 0.07 retained in the config for compatibility. B7 adds a light supervised contrastive term with $\lambda_{\mathrm{supcon}}=0.02$ for the ablation comparison.

\subsection{Checkpoint and Evaluation Protocol}

Evaluation uses the \texttt{best.pt} checkpoint produced by the training script. For every strict Tongji run, \texttt{best.pt} is selected using only the validation split from development palm classes. Held-out gallery and probe samples are not used for checkpoint selection, early stopping, hyperparameter selection, threshold selection, or training-time model comparison. The checkpoint-selection audit reconstructs the selected epoch for each run and confirms that all final strict Tongji checkpoints are selected by validation Rank-1 without gallery/probe/test influence. For B6, the config selects the post-BN embedding for evaluation. Matching is performed with cosine similarity over normalized embeddings. The reported metrics are Rank-1, Rank-5, Macro-F1, EER, TAR@FAR=$10^{-2}$, and TAR@FAR=$10^{-3}$. Verification thresholds are swept over observed cosine scores using \texttt{sklearn.metrics.roc\_curve}; a pair is accepted when its score is greater than or equal to the threshold. EER is computed by interpolating the ROC curve with Brent root finding when possible, with a nearest $|\mathrm{FPR}-\mathrm{FNR}|$ fallback. TAR@FAR is reported at the ROC point whose empirical FPR is nearest to the target FAR. The metric-threshold audit verifies 12,000 genuine and 1,428,000 impostor comparisons per strict Tongji run, corresponding to a minimum empirical FAR step of approximately $7.0\times10^{-7}$. TAR@FAR=$10^{-3}$ is emphasized because it measures strict low-FAR verification behavior.

\subsection{Evaluation Metrics}

Let $x_i \in \mathbb{R}^d$ be the embedding vector extracted for image $i$. Embeddings are $L_2$-normalized: $\hat{x}_i = x_i / \lVert x_i \rVert_2$. The similarity between two images is computed using cosine similarity: $S(\hat{x}_1, \hat{x}_2) = \hat{x}_1^T \hat{x}_2$. The following evaluation metrics are defined:
\begin{itemize}
    \item \textbf{Rank-$k$ Accuracy}: The percentage of probe images for which the true matching identity is within the top-$k$ most similar gallery templates. We report Rank-1 and Rank-5 accuracies.
    \item \textbf{Macro-F1}: For each probe image, the predicted identity is the identity of the nearest gallery template under cosine similarity. Macro-F1 is computed over probe identities from these nearest-gallery predictions to summarize class-balanced identification performance.
    \item \textbf{False Accept Rate (FAR(t))} at similarity threshold $t$: The ratio of impostor pairs incorrectly accepted as genuine matches:
    \begin{equation}
        \mathrm{FAR}(t) = \frac{\#\{\text{Impostor Similarities} \ge t\}}{\#\text{Total Impostor Pairs}}
    \end{equation}
    \item \textbf{False Reject Rate (FRR(t))} at similarity threshold $t$: The ratio of genuine pairs incorrectly rejected:
    \begin{equation}
        \mathrm{FRR}(t) = \frac{\#\{\text{Genuine Similarities} < t\}}{\#\text{Total Genuine Pairs}}
    \end{equation}
    \item \textbf{True Accept Rate (TAR(t))}: The verification rate defined as $1 - \mathrm{FRR}(t)$.
    \item \textbf{Equal Error Rate (EER)}: The error rate at the threshold $t_{\mathrm{EER}}$ where FAR and FRR are equal: $\mathrm{FAR}(t_{\mathrm{EER}}) = \mathrm{FRR}(t_{\mathrm{EER}}) = \mathrm{EER}$.
    \item \textbf{TAR @ FAR}: The True Accept Rate at specific false acceptance rate constraints: $\mathrm{TAR@FAR}=10^{-2}$ and $\mathrm{TAR@FAR}=10^{-3}$.
\end{itemize}

\subsection{Hardware and Software Evidence}

The verified local evidence records CUDA execution on an NVIDIA GeForce RTX 4050 Laptop GPU with 6GB VRAM, PyTorch 2.12.0+cu126, and the Conda environment \texttt{palm\_lgf}. The current repository evidence does not track OS, CPU, or RAM details for the final B6 runs, so those fields are omitted from the paper draft.

\subsection{Reproducibility}

The experiments are configured through YAML files, split JSON files, and scripts in the repository. The relevant training and evaluation entry points are \texttt{scripts/train\_lgf.py} and \texttt{scripts/eval\_embedding.py}. Palm-class-disjoint split construction and audit are supported by \texttt{scripts/make\_tongji\_iitd\_disjoint\_splits.py}, \texttt{scripts/audit\_rankb\_protocol.py}, and \texttt{scripts/validate\_configs.py}. The final evidence index is \texttt{docs/results/README.md}. The final strict ablation outputs are \texttt{docs/results/strict\_tongji\_ablation\_results.md} and \texttt{docs/results/strict\_tongji\_ablation\_runs.csv}; score-tail diagnostics are stored in \texttt{docs/results/strict\_tongji\_score\_diagnostics.md}; paired uncertainty is stored in \texttt{docs/results/paired\_statistics\_b6\_vs\_b1.md} and \texttt{docs/results/paired\_statistics\_component\_ablation.md}. Protocol, checkpoint-selection, identity/parser, gallery/probe-construction, metric-threshold, session-quality, and reference audits are stored in \texttt{docs/audits/rankb\_protocol\_audit.md}, \texttt{docs/audits/checkpoint\_selection\_audit.md}, \texttt{docs/audits/identity\_parser\_audit.md}, \texttt{docs/audits/gallery\_probe\_audit.md}, \texttt{docs/audits/metric\_threshold\_audit.md}, \texttt{docs/audits/tongji\_session\_quality.md}, and \texttt{docs/audits/paper\_reference\_audit.md}. Superseded exploratory summaries are archived under \texttt{docs/legacy\_results/}. Raw segmented data, experiment directories, checkpoint tensors, score tensors, and exported submission zips are not committed; the repository tracks configs, split JSON files, metadata, scripts, audits, and saved result summaries.
