\section{Discussion}

The palm-class-disjoint results change the interpretation of the BNNeck + ArcFace variant. In the original seen-identity Tongji protocol, B6 appears favorable. However, when development and test identities are made palm-class-disjoint, B6 does not outperform the B1 CE + SupCon baseline overall. This difference shows that the evaluation protocol is a first-order determinant of the empirical conclusion.

The main failure mode is not uniform across session directions. B6 has a limited gain at the strict TAR@FAR=$10^{-3}$ operating point in the S1$\rightarrow$S2 direction, but it trails B1 on most other S1$\rightarrow$S2 metrics and underperforms B1 across all reported metrics in S2$\rightarrow$S1. This indicates that angular-margin supervision and BNNeck can shape useful embedding geometry in some settings, but that the effect does not translate reliably to held-out palm classes under both session directions.

The score-tail diagnostics support the same conservative conclusion. Although B5 has the highest observed mean Rank-1 and TAR@FAR=$10^{-3}$ among the strict ablation variants, B1 has the largest d-prime and therefore the highest observed average genuine/impostor separation. This mismatch between separation diagnostics and low-FAR recognition metrics suggests that no single component dominates all operating regimes. The ArcFace-based variants do not provide a consistent score-tail advantage over the CE + SupCon baseline.

The paired uncertainty estimates reinforce this cautious interpretation. Across the six paired Tongji seed-direction units, the mean deltas for B6 relative to B1 are unfavorable on all reported metrics, but most bootstrap intervals remain wide because of the small number of paired units. Thus, the evidence is sufficient to reject a general B6-improvement claim, while remaining too small to support a broad statistical-superiority claim in the opposite direction.



\input{sections/tongji_session_quality_table}


Table~\ref{tab:tongji_session_quality} reports a session-level image-quality audit for Tongji segmented images. Both sessions contain 6000 images, and the average differences between session2 and session1 are small: +1.09 in mean intensity, +0.15 in intensity standard deviation, and +0.21 in Laplacian sharpness. These statistics do not prove that image quality alone causes the directional performance asymmetry. Instead, they support a more cautious interpretation: the two acquisition sessions are measurable but closely matched at the level of simple image-quality summaries, so the observed S1$\rightarrow$S2 versus S2$\rightarrow$S1 differences likely reflect a combination of session shift, identity sampling, and metric-learning sensitivity rather than a single obvious brightness or blur artifact.

The corrected IITD palm-class-disjoint within-session protocol is included as secondary validation, not as cross-session evidence. It shows that B6 is competitive with B1, but not superior: the mean Rank-1 delta is only +0.12 percentage points, while B6 has slightly worse mean EER (+0.19 percentage points) and lower TAR@FAR=$10^{-2}$ and TAR@FAR=$10^{-3}$ (-0.48 and -0.72 percentage points). This reinforces the paper's protocol-sensitive interpretation rather than a general improvement claim.

\subsection{Why Does BNNeck+ArcFace Not Transfer Under the Strict Tongji Protocol?}

The strict Tongji results are consistent with an objective--protocol mismatch rather than a simple failure of either BNNeck or ArcFace. First, ArcFace optimizes angular separation among development palm classes, whereas the primary evaluation uses held-out palm classes and deployment-relevant impostor tails. A classifier geometry that separates the training classes can therefore fail to preserve the same ranking at low-FAR operating points on unseen palms. Second, BNNeck changes the representation used by the classifier versus the retrieval embedding. This separation can be useful, but it can also alter cosine-score calibration under session shift, especially when the post-BN embedding is used for gallery--probe matching. Third, the S1$\rightarrow$S2 and S2$\rightarrow$S1 protocols expose asymmetric acquisition effects. A component that improves or preserves one direction may degrade the other, so a bidirectional mean can hide different genuine/impostor tail behaviors across session order.

This interpretation is not a causal proof. It is a protocol-level explanation consistent with the paired Tongji deltas, directional table, ROC/DET curves, and score-distribution diagnostics: BNNeck+ArcFace appeared favorable in a seen-identity diagnostic setting, but its angular-margin objective did not yield a reliable low-FAR gain under held-out palm-class cross-session evaluation.

These results do not imply that BNNeck or ArcFace are ineffective for palmprint embeddings. They indicate that their benefit is conditioned on protocol design, identity overlap, and session direction. A fair report must therefore distinguish seen-identity evidence from held-out palm-class evidence and should avoid claims of dataset-independent superiority.



\subsection{Limitations}

External benchmark leadership and cross-dataset robustness are not claimed. The fixed-Gabor baseline is included only as a protocol-normalized classical texture reference and should not be interpreted as a reimplementation of Competitive Code, PalmNet, or CompNet. The current evidence is limited to a scoped Tongji cross-session analysis and an IITD within-session secondary validation. The number of paired seed-direction units is small, and most paired intervals for B6 versus B1 cross zero except EER. The score-tail diagnostics, ROC/DET curves, and session-quality audit strengthen the analysis, but they do not replace a verified cross-dataset benchmark or a larger protocol suite. Future work should evaluate additional datasets, add verified cross-dataset protocols, and test whether the direction-specific failure observed on Tongji is due to session image characteristics, split design, or training-objective mismatch.
