\section{Conclusion}

This paper evaluated a ResNet18 + BNNeck + ArcFace embedding model for palmprint recognition under protocols that lead to different empirical conclusions. The method appears favorable relative to the CE + SupCon baseline in the original seen-identity Tongji diagnostic setting, but it does not improve over CE + SupCon overall under the stricter development/test palm-class-disjoint Tongji protocol. In the palm-class-disjoint Tongji evaluation, B6 trails B1 in Rank-1, Rank-5, Macro-F1, EER, and TAR@FAR=$10^{-2}$, and it also trails B1 on the bidirectional average TAR@FAR=$10^{-3}$.

The strict component ablation further shows that B5 has the highest observed mean on the selected Rank-1 and low-FAR TAR criteria, which combines BNNeck with cross-entropy supervision. This indicates that BNNeck can help the embedding geometry, but that ArcFace and light SupCon do not provide a reliable additional gain under the strict Tongji palm-class-disjoint protocol.

The corrected IITD palm-class-disjoint within-session protocol is included as secondary validation. It shows that B6 is near-tied with B1 rather than clearly better: B6 changes Rank-1 by only +0.12 percentage points, has slightly worse EER, and trails at TAR@FAR=$10^{-3}$ by -0.72 percentage points. Together with the primary Tongji cross-session palm-class-disjoint result, this supports the conclusion that the BNNeck + ArcFace recipe is protocol-sensitive rather than generally superior.

The fixed-Gabor reference additionally shows that a palmprint-specific classical texture representation can remain competitive for Rank-1 identification while failing to match learned embeddings at strict low-FAR verification. The final claim is thus scoped. The paper does not claim general superiority, external benchmark leadership, or cross-dataset robustness. It contributes a reproducible protocol-sensitive evaluation and identifies an important limit of transferring seen-identity improvements to palm-class-disjoint cross-session palmprint recognition.
