\documentclass[10pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage[section]{placeins}

\title{Protocol-Sensitive Component Evaluation of BNNeck and ArcFace for Cross-Session Palmprint Recognition}
\author{PALM\_CGK\_BASE Project Team}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Cross-session contactless palmprint recognition requires evaluation protocols that separate acquisition shift from identity memorization and test verification behavior at strict false-acceptance operating points. This paper evaluates ResNet18 palmprint embeddings with cross entropy, supervised contrastive learning, BNNeck, and ArcFace under the original seen-identity Tongji diagnostic setting and a stricter development/test palm-class-disjoint Tongji protocol. The central finding is protocol-sensitive. In the seen-identity diagnostic setting, BNNeck + ArcFace appears favorable relative to the CE + SupCon baseline. Under the stricter Tongji palm-class-disjoint protocol, however, BNNeck + ArcFace does not improve over CE + SupCon overall: its bidirectional three-seed average trails the baseline by 1.18 percentage points in Rank-1 and has an EER that is 1.01 percentage points worse. A strict component ablation further shows that BNNeck + CE, not BNNeck + ArcFace, is the best-performing tested variant on the main Tongji Rank-1 and TAR@FAR=$10^{-3}$ metrics, while ArcFace-based variants are not consistently beneficial. The corrected IITD palm-class-disjoint within-session protocol is included only as secondary validation and shows a near-tie rather than a clear BNNeck + ArcFace improvement. The supported contribution is therefore a scoped protocol-sensitive component evaluation, not a claim of universal method superiority, cross-dataset robustness, or external benchmark leadership.
\end{abstract}



\input{sections/01_introduction}



\input{sections/02_related_work}



\input{sections/03_method}



\input{sections/04_experiments}



\input{sections/05_results}



\input{sections/06_ablation}



\input{sections/07_discussion}



\input{sections/08_conclusion}


\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
